Sequential rank agreement methods for comparison of ranked lists

### 2015-04-27 latex/paper.Rnw
now with description of two benchmarks

\section{Introduction}
Ranking of items or results is common in scientific research and
ranked lists occur as the result of many applications in
statistics. Regression methods rank predictor variables according to
magnitude of association with outcome, prediction models rank subjects
according to their risk of an event, and genetic studies rank genes
according to their difference in gene expression levels across
samples.

@@

Three approaches

>>>>

\section{Introduction}

Ranking of items or results is common in scientific research and
ranked lists occur as the result of many applications in
statistics. Regression methods rank predictor variables according to
magnitude of association with outcome, prediction models rank subjects
according to their risk of an event, and genetic studies rank genes
according to their difference in gene expression levels across
samples.

@@

To interpretate the sequential rank agreement scale we propose by
several different benchmark values. Our data free benchmark value is
obtained by computing the sequential rank agreement of $L$ lists each
containing a permutation of $P$ items. Practically this benchmark
value can be obtained by averaging the result of repeated computer
experiments. In the uncensored case each experiment contains $L$ lists
of random permutations of the numbers $1,\dots,P$. In the censored
case only the uncensored part of the orginal lists is randomly
permuted.

In our experience XX repetitions are sufficient to reduce Monte Carlo
error. Table Appendix A shows benchmark values obtained with

Our no-information benchmark can be applied in situations where each
list is an importance ranking of $P$ predictors resulting from
regression analyses. The idea is to repeat the regression analyses in
modified data where the outcome vector is randomly permuted. This
artificially removes any potential information regarding the
regression that the real data may contain.

- third approach?
